### 2013-11-25 document/ms.tex
'starting' document

\documentclass[12pt,preprint]{aastex}

% has to be before amssymb it seems
\usepackage{color,hyperref}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
            filecolor=linkcolor,urlcolor=linkcolor}

\usepackage{url}
\usepackage{algorithmic,algorithm}
\usepackage{multirow}

\usepackage{listings}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{language=Python,
        basicstyle=\footnotesize\ttfamily,
        showspaces=false,
        showstringspaces=false,
        tabsize=2,
        breaklines=false,
        breakatwhitespace=true,
        identifierstyle=\ttfamily,
        keywordstyle=\bfseries\color[rgb]{0.133,0.545,0.133},
        commentstyle=\color[rgb]{0.133,0.545,0.133},
        stringstyle=\color[rgb]{0.627,0.126,0.941},
    }

\input{vars}

\begin{document}

\title{%
The \kplr\ Catalog:
Systematic probabilistic parameter estimation for all \kepler\ planet
candidates
}

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    \etal
}
\altaffiltext{1}{To whom correspondence should be addressed:
                        \url{danfm@nyu.edu}}
\altaffiltext{\nyu}{Center for Cosmology and Particle Physics,
                        Department of Physics, New York University,
                        4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                        K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\begin{abstract}

In order to study the population of transiting exoplanets found by the
\kerpler\ mission, we must propagate information from ...

\end{abstract}

\keywords{% CUT THESE DOWN TO SIX
  astronomical~databases:~miscellaneous
  ---
  catalogs
  ---
  eclipses
  ---
  methods:~statistical
  ---
  planetary~systems
  ---
  planets~and~satellites:~detection
  ---
  planets~and~satellites:~fundamental~parameters
  ---
  stars:~statistics
  ---
  surveys
}

\section{Introduction}

So probabilistically righteous.

\acknowledgments
It is a pleasure to thank
    Tom Barclay (NASA Ames),
    \ldots
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), and NASA
(grant NNX08AJ48G).

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright

\bibitem[Tremaine \& Dong(2012)]{tremaine}
Tremaine, S., \& Dong, S.\ 2012, \aj, 143, 94
\arxiv{1106.5403}

\end{thebibliography}

\end{document}

### 2013-11-25 document/ms.tex
first pass at an abstract

@@
 Systematic probabilistic parameter estimation for all \kepler\ planet
-candidates
+candidates and inference of the radius distribution
 }
@@
 
-In order to study the population of transiting exoplanets found by the
-\kerpler\ mission, we must propagate information from ...
+We provide a catalog of probabilistic constraints on the physical parameters
+of each of the planet candidates found using data from the \kepler\ transiting
+planet search.
+Using a physically motivated generative model with flat ``default'' priors, we
+draw samples from the posterior probability distribution conditioned on all
+the available light curves from \kepler\ Quarters 0 through 16.
+We release both the catalog values and full posterior samplings for each
+system.
+We compare our results to the existing KOI catalog and find xxx.
+Using these samplings, we demonstrate a computationally tractable hierarchical
+inference technique for simultaneously modeling the exoplanet radius
+distribution and the selection function of the \kepler\ survey and pipeline.
+When applied to a sample of cool stars with well constrained properties, we
+find yyy.
+
+Access to the catalog is available on-line at \url{http://data.kplr.co} and
+the code is available---under the terms of the MIT license---at
+\url{https://github.com/dfm/kois}.
 
@@
     Tom Barclay (NASA Ames),
+    Tim Morton (Princeton),
     \ldots

### 2013-11-25 kois/kois.py
switching to new duration parameterization

@@ -32,7 +32,8 @@ def load_system(koi_id, lc_window_factor=4, sc_window_factor=4,
 
     logging.info("Getting the catalog parameters for KOI {0}.XX"
                  .format(koi_id))
-    kois = sorted(client.koi("{0}.01".format(koi_id)).star.kois,
+    kois = sorted([k for k in client.koi("{0}.01".format(koi_id)).star.kois
+                   if k.koi_disposition in ["CANDIDATE", "CONFIRMED"]],
                   key=lambda k: k.kepoi_name)
     if not len(kois):
         raise RuntimeError("No KOIs listed in the ctalog with ID '{0}'"
@@ -49,14 +50,21 @@ def load_system(koi_id, lc_window_factor=4, sc_window_factor=4,
 
     # Loop over KOIs and add the initial values to the model.
     for koi in kois:
+        # Parse the KOI parameters.
         P = koi.koi_period
+        t0 = koi.koi_time0bk % P
+        ror = koi.koi_ror
+        b = koi.koi_impact
 
         # Skip single transits.
         if P < 0:
             continue
 
-        t0 = koi.koi_time0bk % P
-        model.add_koi(P, t0, koi.koi_duration/24., koi.koi_ror, koi.koi_impact)
+        # Convert the KOI duration to the b=0 duration that we need.
+        tau = (koi.koi_duration/24.) / np.sqrt((1+ror)**2 - b*b)
+
+        # Add the KOI to the model.
+        model.add_koi(P, t0, tau, ror, b)
 
     # Load the light curves.
     logging.info("Loading datasets")

### 2013-11-26 document/ms.tex

@@
 The \kplr\ Catalog:
-Systematic probabilistic parameter estimation for all \kepler\ planet
-candidates and inference of the radius distribution
+Systematic probabilistic parameter estimation for every \kepler\ planet candidate
 }
@@
 
-\begin{abstract}
+\begin{abstract} % should be aims, methods, results
+As precise as \kepler\ is,
+it provides only probabilistic information
+about transiting companions in the lightcurves of stars.
+The official \kepler\ best-fit values for the parameters
+(periods, radii ratios, durations, impact parameters)
+contain some known biases,
+are not associated with full uncertainty propagation,
+and cannot be used as the basis of any probabilistic population analysis.
 
-We provide a catalog of probabilistic constraints on the physical parameters
-of each of the planet candidates found using data from the \kepler\ transiting
+Here we provide a catalog of probabilistic constraints on the physical parameters
+for every planet candidate (KOI) from the \kepler\ transiting
 planet search.
-Using a physically motivated generative model with flat ``default'' priors, we
+Using a physically motivated generative model with flat ``interim'' priors, we
 draw samples from the posterior probability distribution conditioned on all
 the available light curves from \kepler\ Quarters 0 through 16.
-We release both the catalog values and full posterior samplings for each
+We release both the catalog values and full $16384$-element posterior samplings for each
 system.
-We compare our results to the existing KOI catalog and find xxx.
+We compare our results to the existing KOI Catalog and find xxx.
 Using these samplings, we demonstrate a computationally tractable hierarchical

### 2013-11-27 document/ms.tex
duration tweaks

@@
 
+\section{Parameters}
+
+We choose to sample in parameters that are directly informed by the light
+curve instead of the full set of physical parameters in the generative model.
+The motivation for this choice is to attempt to find parameters that are close
+to sufficient statistics for the light curves while being independent of the
+stellar parameters.
+To this end, we chose to parameterize each planet candidate with period
+\period, epoch \epoch, radius \ror\ (measured in stellar radii), impact
+parameter \impact, and transit duration \duration.
+Our specific definition of transit duration deserves some discussion.
+We define the transit duration as the time that it would take for the
+center of the exoplanet to transit the center of the star (at $b=0$) instead
+of choosing one of the standard definitions---for example $T_\mathrm{tot}$
+from \citet{winn}.
+We make the further simplifying assumption that the planet transits in a
+straight line across the face of the star (WORDING).
+In this limit, the conversion between \duration\ and the standard
+$T_\mathrm{tot}$ used in the KOI catalog is
+\begin{eqnarray}
+T_\mathrm{tot} \approx \duration \, \sqrt{(1+\ror)^2 - \impact^2}
+\end{eqnarray}
+
+\section{Comments}
+
+\begin{itemize}
+\item{Limb darkening}
+\item{Integration over exposure time}
+\end{itemize}
+
 \acknowledgments
@@
 
+\bibitem[Winn(2010)]{winn}
+Winn, J.~N.\ 2010, \arxiv{1001.2010}
+
 \end{thebibliography}

### 2013-11-27 kois/kois.py
default to solar teff

@@ -33,7 +33,8 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
                            .format(kepid))
 
     # Set up the initial limb-darkening profile.
-    mu1, mu2 = get_quad_coeffs(kois[0].koi_steff)
+    teff = kois[0].koi_steff
+    mu1, mu2 = get_quad_coeffs(teff if teff is not None else 5778)
     mu1 = max(0.0, mu1)
     ldp = bart.ld.QuadraticLimbDarkening(mu1, mu2, ldp_nbins)
 

### 2013-11-27 kois/kois.py
correct koi name and set pythonpath

@@ -94,7 +94,7 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
     if not len(datasets):
         raise RuntimeError("No datasets could be de-trended.")
 
-    return kois[0].kepoi_name.split(".")[0], model
+    return int(kois[0].kepoi_name.split(".")[0][1:]), model
 
 
 class KOILightCurve(LightCurve):

### 2013-11-28 kois/kois.py
need more data to detrend

@@ -106,10 +106,10 @@ class KOILightCurve(LightCurve):
             hp = 0.5 * p
             m[np.abs((t - t0 + hp) % p - hp) < dt] = 0
 
-        if not np.sum(m):
+        if np.sum(m) < 20:
             return False
 
-        p = np.polyfit(t[m], self.flux[m], order)  # , w=self.ivar[m])
+        p = np.polyfit(t[m], self.flux[m], order, w=self.ivar[m])
         self.flux /= np.polyval(p, t)
         return True
 

### 2013-11-28 kois/kois.py
adding pbs templates

@@ -43,6 +43,7 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
                   period_tol=sc_window_factor*3e-4)
 
     # Loop over KOIs and add the initial values to the model.
+    full_durations = np.array([])
     for koi in kois:
         # Parse the KOI parameters.
         P = koi.koi_period
@@ -55,6 +56,7 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
             continue
 
         # Convert the KOI duration to the b=0 duration that we need.
+        full_durations = np.append(full_durations, koi.koi_duration/24.)
         tau = (koi.koi_duration/24.) / np.sqrt((1+ror)**2 - b*b)
 
         # Add the KOI to the model.
@@ -76,7 +78,7 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
                              data["PDCSAP_FLUX_ERR"][m], texp=texp,
                              K=5 if lc.sci_archive_class == "CLC" else 3)
         datasets += (data.active_window(model.periods, model.epochs,
-                                        factor*model.durations)
+                                        factor*full_durations)
                      .autosplit())
 
     # Remove datasets with not enough data points.
@@ -89,7 +91,7 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
     model.datasets += [d for d in datasets
                        if d.remove_polynomial(model.periods, model.epochs,
                                               detrend_window_factor
-                                              * model.durations, poly_order)]
+                                              * full_durations, poly_order)]
     logging.info("{0} datasets were de-trended".format(len(model.datasets)))
     if not len(datasets):
         raise RuntimeError("No datasets could be de-trended.")
@@ -106,7 +108,7 @@ class KOILightCurve(LightCurve):
             hp = 0.5 * p
             m[np.abs((t - t0 + hp) % p - hp) < dt] = 0
 
-        if np.sum(m) < 20:
+        if np.sum(m) < 10:
             return False
 
         p = np.polyfit(t[m], self.flux[m], order, w=self.ivar[m])

### 2013-11-29 plot.py
batch scripts

@@ -1,0 +1,24 @@
+import os
+import subprocess
+from multiprocessing import Pool
+
+
+def run_process(kid):
+    if os.path.exists("models/{0}/mcmc.txt".format(kid)):
+        return None
+    cmd = "scripts/kois-fetch-results {0}".format(kid)
+    print("Running: {0}".format(cmd))
+    subprocess.check_call(cmd, shell=True)
+
+    cmd = "scripts/kois-plot-results {0} -b 20000".format(kid)
+    print("Running: {0}".format(cmd))
+    subprocess.check_call(cmd, shell=True)
+
+    print("FINISHED {0}".format(kid))
+    return kid
+
+
+pool = Pool()
+results = pool.map(run_process,
+                   [int(line.split()[0]) for line in open("targets/kois.txt")])
+print("\n".join(map(str, [r for r in results if r is not None])))

### 2013-11-29 run.py

@@ -1,0 +1,13 @@
+import subprocess
+from multiprocessing import Pool
+
+
+def run_process(kid):
+    cmd = "scripts/kois-build-model -c butinah --submit {0}".format(kid)
+    print("Running: {0}".format(cmd))
+    subprocess.check_call(cmd, shell=True)
+
+
+pool = Pool()
+pool.map(run_process,
+         [int(line.split()[0]) for line in open("targets/kois.txt")])

### 2013-12-04 kois/ld.py
safety

@@ -47,14 +47,14 @@ class QuadraticLimbDarkening(object):
     @property
     def coeffs(self):
         q1, q2 = self._q1, self._q2
-        q1 = np.sqrt(q1)
+        q1 = np.sqrt(np.abs(q1))
         return 2*q1*q2, q1*(1-2*q2)
 
     @coeffs.setter
     def coeffs(self, value):
         u1, u2 = value
         u2 = u1+u2
-        self._q1, self.q2 = u2*u2, 0.5*u1/u2
+        self.q1, self.q2 = u2*u2, 0.5*u1/u2
 
     @property
     def intensity(self):

### 2013-12-04 kois/lightcurve.c
dealing with b > 1+r

@@ -115,43 +115,46 @@ void lightcurve (int n, double *t, int K, double texp, int np,
         hpmt0 = hp - t0;
         duration = durations[k];
 
-        // // Compute the velocity based on the b=0 duration.
-        // v = 2.0 / duration;
-        //
-        // // Compute the b=impact transit time.
-        // delta_t = sqrt(opr2 - b*b) / v;
+        // Skip planets with no transits.
+        if (opr2 > b2) {
+            // // Compute the velocity based on the b=0 duration.
+            // v = 2.0 / duration;
+            //
+            // // Compute the b=impact transit time.
+            // delta_t = sqrt(opr2 - b2) / v;
 
-        // FIXME.
-        delta_t = 0.5 * duration;
-        v = 2 * sqrt(opr2 - b*b) / duration;
+            // FIXME.
+            delta_t = 0.5 * duration;
+            v = 2 * sqrt(opr2 - b2) / duration;
 
-        // Compute the impact parameter as a function of time.
-        for (i = 0; i < ntot; ++i) {
-            // Find the time since transit.
-            t1 = fmod(ttmp[i] + hpmt0, P) - hp;
+            // Compute the impact parameter as a function of time.
+            for (i = 0; i < ntot; ++i) {
+                // Find the time since transit.
+                t1 = fmod(ttmp[i] + hpmt0, P) - hp;
 
-            // If the planet is in transit, compute the impact parameter.
-            if (fabs(t1) < delta_t) {
-                t1 *= v;
-                btmp[i] = sqrt(b2 + t1*t1);
-                sgn[i] = 1;
-            } else sgn[i] = -1;
-        }
-
-        // Compute the light curve.
-        lightcurve_one (rors[k], nbins, r, ir, ntot, btmp, sgn, ftmp);
-
-        // Integrate over exposure time.
-        if (K > 1) {
-            for (i = 0; i < n; ++i) {
-                v = 0.0;
-                for (j = 0; j < K; ++j)
-                    v += ftmp[i*K+j];
-                f[i] *= v / K;
+                // If the planet is in transit, compute the impact parameter.
+                if (fabs(t1) < delta_t) {
+                    t1 *= v;
+                    btmp[i] = sqrt(b2 + t1*t1);
+                    sgn[i] = 1;
+                } else sgn[i] = -1;
             }
-        } else {
-            for (i = 0; i < n; ++i)
-                f[i] *= ftmp[i];
+
+            // Compute the light curve.
[…]

### 2013-12-05 kois/lightcurve.c
ld speedup

@@ -54,13 +54,6 @@ void lightcurve_one (double p, int nbins, double *r, double *ir, int n,
     int i, j;
     double *areas = malloc(nbins * sizeof(double));
 
-    // First, compute the normalization constant by integrating over the face
-    // of the star.
-    double norm = ir[0] * r[0] * r[0];
-    for (i = 1; i < nbins; ++i)
-        norm += ir[i] * (r[i] * r[i] - r[i - 1] * r[i - 1]);
-    norm *= M_PI;
-
     // Compute the fraction of un-occulted flux for each time sample.
     for (i = 0; i < n; ++i) {
         if (sgn[i] >= 0) {
@@ -74,7 +67,7 @@ void lightcurve_one (double p, int nbins, double *r, double *ir, int n,
             lam[i] = areas[0] * ir[0];
             for (j = 1; j < nbins; ++j)
                 lam[i] += ir[j] * (areas[j] - areas[j - 1]);
-            lam[i] = 1.0 - lam[i] / norm;
+            lam[i] = 1.0 - lam[i];
         } else lam[i] = 1.0;
     }
 
@@ -90,8 +83,17 @@ void lightcurve (int n, double *t, int K, double texp, int np,
     int i, j, k, ntot = n * K, *sgn = malloc(ntot * sizeof(int));
     double t1, delta_t, v, b, b2, opr2, t0, P, hp, hpmt0, duration,
            *ttmp,
+           *irtmp = malloc(nbins * sizeof(double)),
            *ftmp = malloc(ntot * sizeof(double)),
            *btmp = malloc(ntot * sizeof(double));
+
+    // First, compute the normalization constant by integrating over the face
+    // of the star.
+    double norm = ir[0] * r[0] * r[0];
+    for (i = 1; i < nbins; ++i)
+        norm += ir[i] * (r[i] * r[i] - r[i - 1] * r[i - 1]);
+    norm *= M_PI;
+    for (i = 0; i < nbins; ++i) irtmp[i] = ir[i] / norm;
 
     if (K > 1) ttmp = malloc(ntot * sizeof(double));
     else ttmp = t;
@@ -141,7 +143,7 @@ void lightcurve (int n, double *t, int K, double texp, int np,
             }
 
             // Compute the light curve.
-            lightcurve_one (rors[k], nbins, r, ir, ntot, btmp, sgn, ftmp);
[…]

### 2013-12-07 document/ms.tex
added outline material

@@
 
-\section{Parameters}
+\section{Data}
+
+Kepler data here.
+
+Cut out bits around the transits, masking, etc.
+
+Pre-conditioning by doing the local linear fits.
+
+What gets passed forward:  Flattened light curve bits plus ivars?
+
+\section{Model}
+
+A model, from our perspective,
+is a parameterized probability for the data,
+and a prior probability distribution over parameters.
+For the probability of the data, we do [XXX chi-squared].
 

### 2013-12-11 kois/_kois.c
switching to mandel and agol style light curve

@@ -19,12 +19,12 @@ static struct module_state _state;
 PyObject *kois_light_curve (PyObject *self, PyObject *args)
 {
     int K;
-    double texp;
+    double texp, mu1, mu2;
     PyObject *t_obj, *periods_obj, *epochs_obj, *durations_obj,
-             *rors_obj, *impacts_obj, *r_obj, *ir_obj;
-    if (!PyArg_ParseTuple(args, "OidOOOOOOO", &t_obj, &K, &texp, &periods_obj,
+             *rors_obj, *impacts_obj;
+    if (!PyArg_ParseTuple(args, "OidOOOOOdd", &t_obj, &K, &texp, &periods_obj,
                           &epochs_obj, &durations_obj, &rors_obj,
-                          &impacts_obj, &r_obj, &ir_obj))
+                          &impacts_obj, &mu1, &mu2))
         return NULL;
 
     PyArrayObject *t_array = PARSE_ARRAY(t_obj),
@@ -32,13 +32,10 @@ PyObject *kois_light_curve (PyObject *self, PyObject *args)
                   *epochs_array = PARSE_ARRAY(epochs_obj),
                   *durations_array = PARSE_ARRAY(durations_obj),
                   *rors_array = PARSE_ARRAY(rors_obj),
-                  *impacts_array = PARSE_ARRAY(impacts_obj),
-                  *r_array = PARSE_ARRAY(r_obj),
-                  *ir_array = PARSE_ARRAY(ir_obj);
+                  *impacts_array = PARSE_ARRAY(impacts_obj);
 
     int n = (int) PyArray_DIM(t_array, 0),
-        np = (int) PyArray_DIM(periods_array, 0),
-        nld = (int) PyArray_DIM(r_array, 0);
+        np = (int) PyArray_DIM(periods_array, 0);
 
     npy_intp dim[1] = {n};
     PyArrayObject *flux_array =
@@ -50,12 +47,10 @@ PyObject *kois_light_curve (PyObject *self, PyObject *args)
            *durations = PyArray_DATA(durations_array),
            *rors = PyArray_DATA(rors_array),
            *impacts = PyArray_DATA(impacts_array),
-           *r = PyArray_DATA(r_array),
-           *ir = PyArray_DATA(ir_array),
            *f = PyArray_DATA(flux_array);
 
     lightcurve (n, t, K, texp, np, periods, epochs, durations, rors, impacts,
[…]

### 2013-12-11 kois/kois.py

@@ -71,7 +71,10 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
     lcs = koi.get_light_curves()
     datasets = []
     for lc in lcs:
-        data = lc.read()
+        try:
+            data = lc.read()
+        except:
+            continue
         m = data["SAP_QUALITY"] == 0
         texp = (kplr.EXPOSURE_TIMES[1] if lc.sci_archive_class == "CLC"
                 else kplr.EXPOSURE_TIMES[0])
@@ -163,9 +166,10 @@ class Model(object):
         self.initial_durations = np.array(self.durations)
 
     def get_light_curve(self, t, K=1, texp=0):
+        mu1, mu2 = self.ldp.coeffs
         return _kois.light_curve(t, K, texp, self.periods, self.epochs,
                                  self.durations, self.rors, self.impacts,
-                                 self.ldp.bins, self.ldp.intensity)
+                                 mu1, mu2)
 
     def lnlike(self):
         return sum([lc.lnlike(self.get_light_curve(lc.time, lc.K, lc.texp))

### 2013-12-11 kois/lightcurve.c

@@ -2,112 +2,35 @@
 #include <stdio.h>
 #include <stdlib.h>
 #include "lightcurve.h"
-
-//
-// Compute the area of a "star" occulted by a "planet".
-//
-// :param double r0:     The radius of the "star".
-// :param double p:      The radius of the "planet".
-// :param double b:      The impact parameter or center-to-center distance.
-//
-// :returns double area: The occulted area.
-//
-double lightcurve_occ_area (double r0, double p, double b)
-{
-    double r2, p2, b2, k1, k2, k3;
-
-    if (b >= r0 + p) return 0.0;
-    else if (b <= r0 - p) return M_PI * p * p;
-    else if (b <= p - r0) return M_PI * r0 * r0;
-
-    r2 = r0 * r0;
-    p2 = p * p;
-    b2 = b * b;
-
-    k1 = acos(0.5 * (b2 + p2 - r2) / b / p);
-    k2 = acos(0.5 * (b2 + r2 - p2) / b / r0);
-    k3 = sqrt((p+r0-b) * (b+p-r0) * (b-p+r0) * (b+r0+p));
-
-    return p2 * k1 + r2 * k2 - 0.5 * k3;
-}
-
-//
-// Compute the limb darkened light curve for a transiting and eclipsing
-// planet.
-//
-// :param double p:         The radius of the planet in stellar radii.
-// :param int nbins:        The number of bins in the limb darkening profile.
-// :param double r[nbins]:  The bin edges in the limb darkening profile
-//                          measured in stellar radii.
-// :param double ir[nbins]: The (relative) values of the limb darkening
-//                          profile in the bins.
-// :param int n:            The number of impact parameters to compute.
-// :param double b[n]:      The values of impact parameter in stellar radii.
-// :param int sgn[n]:       The relative position of the planet. If
-//                          ``sgn[n] >= 0`` then the planet is transiting and
-//                          if ``sgn[n] < 0`` the planet is being eclipsed.
-// :param double lam[n]:    The output relative light curve.
-//
-void lightcurve_one (double p, int nbins, double *r, double *ir, int n,
-                     double *b, int *sgn, double *lam)
-{
-    int i, j;
-    double *areas = malloc(nbins * sizeof(double));
-
-    // Compute the fraction of un-occulted flux for each time sample.
[…]

### 2013-12-11 kois/lightcurve.h

@@ -3,8 +3,8 @@
 
 void lightcurve (int n, double *t, int K, double texp, int np,
                  double *periods, double *epochs, double *durations,
-                 double *rors, double *impacts, int nbins, double *r,
-                 double *ir, double *f);
+                 double *rors, double *impacts, double mu1, double mu2,
+                 double *f);
 
 #endif
 // _LIGHTCURVE_H_

### 2013-12-11 kois/quad.cpp

@@ -1,0 +1,177 @@
+#include <cmath>
+#include <cfloat>
+#include <boost/math/special_functions/ellint_3.hpp>
+#include "quad.h"
+
+/* #define VERBOSE */
+
+using boost::math::ellint_1;
+using boost::math::ellint_2;
+using boost::math::ellint_3;
+
+#define LAMBDA_1 { \
+    double k = sqrt(0.25*(1-a)/(z*p)); \
+    ld = ( ((1-b)*(2*b+a-3)-3*q*(b-2))*ellint_1<double>(k) \
+           + 4*p*z*(z2+7*p2-4)*ellint_2<double>(k) \
+           - 3*q/a*ellint_3<double, double>(-k, (a-1)/a) ) \
+         / (9*M_PI*sqrt(p*z)); \
+}
+
+#define LAMBDA_2 { \
+    double ik = sqrt(4*(z*p)/(1-a)); \
+    ld = 2*(  \
+            (1-5*z2+p2+q*q)*ellint_1<double>(ik) \
+            + (1-a)*(z2+7*p2-4)*ellint_2<double>(ik) \
+            - 3*q/a*ellint_3<double, double>(-ik, (a-b)/a) \
+           ) / (9*M_PI*sqrt(1-a)); \
+}
+
+#define LAMBDA_3 { \
+    double hip = 0.5/p; \
+    ld = 1.0/3 + (16*p*(2*p2-1)*ellint_2<double>(hip) \
+         - (1-4*p2)*(3-8*p2)/p*ellint_1<double>(hip) )/(9*M_PI); \
+}
+
+#define LAMBDA_4 { \
+    double twop = 2*p; \
+    ld = 1.0/3 + 2*( \
+            4*(2*p2-1)*ellint_2<double>(twop) \
+            + (1-4*p2)*ellint_1<double>(twop) \
+         ) / (9*M_PI); \
+}
+
+#define LAMBDA_5 { \
+    ld = 2*acos(1-2*p)/(3*M_PI) - 4*(3+2*p-8*p2)*sqrt(p*(1-p))/(9*M_PI); \
+    if (z < p) ld -= 2.0/3; \
+}
+
+#define LAMBDA_6 { \
+    ld = -2*(1-p2)*sqrt(1-p2)/3; \
+}
+
+#define ETA_2 { \
+    eta = 0.5*p2*(p2+2*z2); \
+}
+
+#define ETA_1 { \
+    ETA_2; \
[…]

### 2013-12-11 kois/quad.h

@@ -1,0 +1,14 @@
+#ifndef _QUAD_H_
+#define _QUAD_H_
+
+#ifdef __cplusplus
+extern "C" {
+#endif
+
+double ldlc (double p, double z, double u1, double u2);
+
+#ifdef __cplusplus
+}
+#endif
+
+#endif

### 2013-12-11 setup.py

@@ -9,7 +9,8 @@ includes = [
     numpy.get_include(),
 ]
 
-kois = Extension("kois._kois", ["kois/_kois.c", "kois/lightcurve.c"],
+kois = Extension("kois._kois", ["kois/_kois.c", "kois/lightcurve.c",
+                                "kois/quad.cpp"],
                  include_dirs=includes)
 
 setup(

### 2013-12-11 kois/kois.py
proper prior on durations

@@ -188,7 +188,7 @@ class Model(object):
             return -np.inf
         if np.any(self.impacts < 0) or np.any(self.impacts > 2):
             return -np.inf
-        if np.any(self.durations < 0):
+        if np.any(self.durations < 0) or np.any(self.durations > 10):
             return -np.inf
         if np.any(self.rors < 0) or np.any(self.rors > 1):
             return -np.inf

### 2013-12-11 kois/kois.py
1/ror^2 prior

@@ -66,6 +66,7 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
         # Add the KOI to the model.
         model.add_koi(P, t0, tau, ror, b)
 
+
     # Load the light curves.
     logging.info("Loading datasets")
     lcs = koi.get_light_curves()
@@ -80,12 +81,15 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
                 else kplr.EXPOSURE_TIMES[0])
         factor = (lc_window_factor if lc.sci_archive_class == "CLC"
                   else sc_window_factor)
+        window = np.array([max(factor*d,
+                           lc_window_factor*d+5*kplr.EXPOSURE_TIMES[1]/86400.)
+                           for d in full_durations])
         data = KOILightCurve(data["TIME"][m],
                              data["PDCSAP_FLUX"][m],
                              data["PDCSAP_FLUX_ERR"][m], texp=texp,
                              K=5 if lc.sci_archive_class == "CLC" else 3)
         datasets += (data.active_window(model.periods, model.epochs,
-                                        factor*full_durations)
+                                        window)
                      .autosplit())
 
     # Remove datasets with not enough data points.
@@ -190,7 +194,7 @@ class Model(object):
             return -np.inf
         if np.any(self.durations < 0) or np.any(self.durations > 10):
             return -np.inf
-        if np.any(self.rors < 0) or np.any(self.rors > 1):
+        if np.any(self.rors < 1e-4) or np.any(self.rors > 1):
             return -np.inf
 
         # Priors based on trimming of the datasets.
@@ -202,7 +206,7 @@ class Model(object):
                   self.period_tol * self.initial_durations):
             return -np.inf
 
-        return 0.0
+        return -2*np.sum(np.log(self.rors))
 
     def lnprob(self):
         lp = self.lnprior()

### 2013-12-11 setup.py

@@ -6,6 +6,7 @@ from setuptools import setup, Extension
 
 includes = [
     "kois",
+    "boost_1_55_0",
     numpy.get_include(),
 ]
 

### 2013-12-12 document/ms.tex
document: inferring the empirical radius distribution

@@
 
+\section{The empirical radius distribution}
+
+The problem of determining the empirical distribution of exoplanet radii
+without taking selection effects into account (see Foreman-Mackey \etal\ in
+prep), can be written as a hierarchical inference problem.
+We have samples from the posterior probability distribution
+\begin{eqnarray}
+z^{(j)} &\sim& p(z\,|\,x,\,\alpha_0)
+\end{eqnarray}
+where $z$ is the radius ratio, $x$ is the light curve, and $\alpha_0$ are the
+parameters of the interim prior $p(z\,|\,\alpha_0)$.
+Instead, we would like to compute and/or sample the parameters describing the
+distribution of physical radii $p(r\,|\,\alpha)$.
+To do this, we must compute the \emph{marginalized likelihood}
+\begin{eqnarray}\eqlabel{marg-like}
+p(x,\,\hat{R}\,|\,\alpha) &=&
+    \int \dd r\dd R\dd z\,\prod_n p(R_n)\,p(\hat{R}_n\,|\,R_n)
+        \prod_k p(r_{nk}\,|\,\alpha)\,p(z_{nk}\,|\,R_n,\,r_{nk})\,
+                p(x\,|\,z_{nk}) \quad.
+\end{eqnarray}
+We can rewrite the inner term---using the fact that
+$p(z_{nk}\,|\,R_n,\,r_{nk})\equiv\delta(r_{nk}-R_n\cdot z_{nk})$---as
+\begin{eqnarray}
+p_{nk}(x\,|\,R_n,\,\alpha)&=&
+\int \dd r_{nk}\dd z_{nk}\,p(r_{nk}\,|\,\alpha)\,p(z_{nk}\,|\,R_n,\,r_{nk})\,
+        p(x\,|\,z_{nk}) \nonumber\\
+&=&
+\int \dd z_{nk}\,p(z_{nk} \cdot R_n\,|\,\alpha)\,p(x\,|\,z_{nk}) \nonumber\\
+&=&
+\int \dd z_{nk}\,p(z_{nk}\cdot R_n\,|\,\alpha)\,p(x\,|\,z_{nk})\,
+\frac{p(z_{nk}\,|\,x,\,\alpha_0)}{p(z_{nk}\,|\,x,\,\alpha_0)} \nonumber\\
+&\propto&
+\int \dd z_{nk}\,\frac{p(z_{nk}\cdot R_n\,|\,\alpha)}{p(z_{nk}\,|\,\alpha_0)}\,
+p(z_{nk}\,|\,x,\,\alpha_0) \nonumber\\
+&\approx&
+\frac{1}{J_{nk}}
+\sum_j \frac{p(z_{nk}^{(j)}\cdot R_n\,|\,\alpha)}{p(z_{nk}^{(j)}\,|\,\alpha_0)}
+\end{eqnarray}
+
+The integral over stellar radius can also be approximated using posterior
+samples
+\begin{eqnarray}
+R^{(l)} &\sim& p(R\,|\,\hat{R}) \quad.
+\end{eqnarray}
+Here, we're not trying to simultaneously infer the distribution of stellar
+parameters.
+This simplifies matters and the full integral in \eq{marg-like} can be
+approximated as
+\begin{eqnarray}
+\frac{p(x,\,\hat{R}\,|\,\alpha)}{p(x,\,\hat{R}\,|\,\alpha_0)}
+&\approx& \prod_n \frac{1}{L_n} \sum_{l=1}^{L_n} \prod_k
+\frac{1}{J_{nk}} \sum_{j=1}^{J_{nk}}
+\frac{p(z_{nk}^{(j)}\cdot R_n\,|\,\alpha)}{p(z_{nk}^{(j)}\,|\,\alpha_0)}
+\quad.
+\end{eqnarray}
+This ratio can now be computed efficiently for different values $\alpha$ and
+optimized or you can set priors $p(\alpha)$ and sample.
+
 \acknowledgments

### 2013-12-25 kois/lightcurve.c
recursively integrate exposure times for fun and profit

@@ -4,79 +4,65 @@
 #include "lightcurve.h"
 #include "quad.h"
 
+#define LC_FACTOR 0.166666666666666666666666666
+
+double lc_evaluate_one (double t, double p, double t0, double tau, double ror,
+                        double b, double mu1, double mu2)
+{
+    double opr = 1+ror, hp = 0.5*p, x;
+    if (b >= opr) return 1.0;
+    x = 2*(fmod(t+hp-t0, p)-hp)*sqrt(opr*opr - b*b)/tau;
+    x = ldlc(ror, sqrt(b*b + x*x), mu1, mu2);
+    return x;
+}
+
+double lc_evaluate (double t, int np, double *periods, double *epochs,
+                    double *durations, double *rors, double *impacts,
+                    double mu1, double mu2)
+{
+    int k;
+    double f = 1.0;
+    for (k = 0; k < np; ++k)
+        f *= lc_evaluate_one(t, periods[k], epochs[k], durations[k], rors[k],
+                             impacts[k], mu1, mu2);
+    return f;
+}
+
+double lc_integrate (double t, double f0, double texp, int np,
+                     double *periods, double *epochs, double *durations,
+                     double *rors, double *impacts, double mu1, double mu2,
+                     double tol, int max_depth, int depth)
+{
+    double tp = t+LC_FACTOR*texp,
+           tm = t-LC_FACTOR*texp,
+           fp = lc_evaluate (tp, np, periods, epochs, durations,
+                             rors, impacts, mu1, mu2),
+           fm = lc_evaluate (tm, np, periods, epochs, durations,
+                             rors, impacts, mu1, mu2);
+    double d = fabs(fp- 2*f0 + fm);
+    if (d > tol && depth < max_depth) {
+        fp = lc_integrate(tp, fp, texp/3.0, np, periods, epochs, durations,
+                          rors, impacts, mu1, mu2, tol, depth+1, max_depth);
+        f0 = lc_integrate(t, f0, texp/3.0, np, periods, epochs, durations,
+                          rors, impacts, mu1, mu2, tol, depth+1, max_depth);
+        fm = lc_integrate(tm, fm, texp/3.0, np, periods, epochs, durations,
+                          rors, impacts, mu1, mu2, tol, depth+1, max_depth);
+    }
+    return (f0+fp+fm) / 3.0;
+}
+
 void lightcurve (int n, double *t, int K, double texp, int np,
[…]

### 2013-12-25 kois/_kois.c
control recursive tolerence from Python

@@ -18,13 +18,13 @@ static struct module_state _state;
 
 PyObject *kois_light_curve (PyObject *self, PyObject *args)
 {
-    int K;
-    double texp, mu1, mu2;
+    int K, max_depth;
+    double texp, mu1, mu2, tol;
     PyObject *t_obj, *periods_obj, *epochs_obj, *durations_obj,
              *rors_obj, *impacts_obj;
-    if (!PyArg_ParseTuple(args, "OidOOOOOdd", &t_obj, &K, &texp, &periods_obj,
+    if (!PyArg_ParseTuple(args, "OidOOOOOdddi", &t_obj, &K, &texp, &periods_obj,
                           &epochs_obj, &durations_obj, &rors_obj,
-                          &impacts_obj, &mu1, &mu2))
+                          &impacts_obj, &mu1, &mu2, &tol, &max_depth))
         return NULL;
 
     PyArrayObject *t_array = PARSE_ARRAY(t_obj),
@@ -50,7 +50,7 @@ PyObject *kois_light_curve (PyObject *self, PyObject *args)
            *f = PyArray_DATA(flux_array);
 
     lightcurve (n, t, K, texp, np, periods, epochs, durations, rors, impacts,
-                mu1, mu2, f);
+                mu1, mu2, tol, max_depth, f);
 
     Py_DECREF(t_array);
     Py_DECREF(periods_array);

### 2013-12-25 kois/kois.py

@@ -66,7 +66,6 @@ def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
         # Add the KOI to the model.
         model.add_koi(P, t0, tau, ror, b)
 
-
     # Load the light curves.
     logging.info("Loading datasets")
     lcs = koi.get_light_curves()
@@ -132,7 +131,8 @@ class KOILightCurve(LightCurve):
 
 class Model(object):
 
-    def __init__(self, ldp, epoch_tol=1.0, period_tol=7e-4):
+    def __init__(self, ldp, epoch_tol=1.0, period_tol=7e-4, tol=1e-7,
+                 max_depth=4):
         self.ldp = ldp
         self.datasets = []
 
@@ -144,6 +144,9 @@ class Model(object):
 
         self.epoch_tol = epoch_tol
         self.period_tol = period_tol
+
+        self.tol = tol
+        self.max_depth = max_depth
 
     @property
     def vector(self):
@@ -173,7 +176,7 @@ class Model(object):
         mu1, mu2 = self.ldp.coeffs
         return _kois.light_curve(t, K, texp, self.periods, self.epochs,
                                  self.durations, self.rors, self.impacts,
-                                 mu1, mu2)
+                                 mu1, mu2, self.tol, self.max_depth)
 
     def lnlike(self):
         return sum([lc.lnlike(self.get_light_curve(lc.time, lc.K, lc.texp))

### 2013-12-25 kois/lightcurve.c

@@ -54,7 +54,7 @@ double lc_integrate (double t, double f0, double texp, int np,
 void lightcurve (int n, double *t, int K, double texp, int np,
                  double *periods, double *epochs, double *durations,
                  double *rors, double *impacts, double mu1, double mu2,
-                 double *f)
+                 double tol, int max_depth, double *f)
 {
     int i;
     double f0;
@@ -63,6 +63,6 @@ void lightcurve (int n, double *t, int K, double texp, int np,
         f0 = lc_evaluate(t[i], np, periods, epochs, durations, rors, impacts,
                          mu1, mu2);
         f[i] = lc_integrate(t[i], f0, texp, np, periods, epochs, durations,
-                            rors, impacts, mu1, mu2, 1e-7, 0, 4);
+                            rors, impacts, mu1, mu2, tol, 0, max_depth);
     }
 }

### 2013-12-25 kois/lightcurve.h

@@ -4,7 +4,7 @@
 void lightcurve (int n, double *t, int K, double texp, int np,
                  double *periods, double *epochs, double *durations,
                  double *rors, double *impacts, double mu1, double mu2,
-                 double *f);
+                 double tol, int max_depth, double *f);
 
 #endif
 // _LIGHTCURVE_H_

### 2013-12-25 kois/_kois.c
sample inividual kois and batch update the MCMC chain

@@ -18,11 +18,11 @@ static struct module_state _state;
 
 PyObject *kois_light_curve (PyObject *self, PyObject *args)
 {
-    int K, max_depth;
+    int max_depth;
     double texp, mu1, mu2, tol;
     PyObject *t_obj, *periods_obj, *epochs_obj, *durations_obj,
              *rors_obj, *impacts_obj;
-    if (!PyArg_ParseTuple(args, "OidOOOOOdddi", &t_obj, &K, &texp, &periods_obj,
+    if (!PyArg_ParseTuple(args, "OdOOOOOdddi", &t_obj, &texp, &periods_obj,
                           &epochs_obj, &durations_obj, &rors_obj,
                           &impacts_obj, &mu1, &mu2, &tol, &max_depth))
         return NULL;
@@ -49,7 +49,7 @@ PyObject *kois_light_curve (PyObject *self, PyObject *args)
            *impacts = PyArray_DATA(impacts_array),
            *f = PyArray_DATA(flux_array);
 
-    lightcurve (n, t, K, texp, np, periods, epochs, durations, rors, impacts,
+    lightcurve (n, t, texp, np, periods, epochs, durations, rors, impacts,
                 mu1, mu2, tol, max_depth, f);
 
     Py_DECREF(t_array);

### 2013-12-25 kois/kois.py

@@ -174,7 +174,7 @@ class Model(object):
 
     def get_light_curve(self, t, K=1, texp=0):
         mu1, mu2 = self.ldp.coeffs
-        return _kois.light_curve(t, K, texp, self.periods, self.epochs,
+        return _kois.light_curve(t, texp, self.periods, self.epochs,
                                  self.durations, self.rors, self.impacts,
                                  mu1, mu2, self.tol, self.max_depth)
 

### 2013-12-25 kois/lightcurve.c

@@ -51,7 +51,7 @@ double lc_integrate (double t, double f0, double texp, int np,
     return (f0+fp+fm) / 3.0;
 }
 
-void lightcurve (int n, double *t, int K, double texp, int np,
+void lightcurve (int n, double *t, double texp, int np,
                  double *periods, double *epochs, double *durations,
                  double *rors, double *impacts, double mu1, double mu2,
                  double tol, int max_depth, double *f)

### 2013-12-25 kois/lightcurve.h

@@ -1,7 +1,7 @@
 #ifndef _LIGHTCURVE_H_
 #define _LIGHTCURVE_H_
 
-void lightcurve (int n, double *t, int K, double texp, int np,
+void lightcurve (int n, double *t, double texp, int np,
                  double *periods, double *epochs, double *durations,
                  double *rors, double *impacts, double mu1, double mu2,
                  double tol, int max_depth, double *f);

### 2013-12-26 kois/kois.py
sampling mean stellar flux

@@ -4,109 +4,11 @@
 from __future__ import (division, print_function, absolute_import,
                         unicode_literals)
 
-__all__ = ["load_system", "LightCurve", "Model"]
+__all__ = ["LightCurve", "Model"]
 
-import logging
 import numpy as np
-
-import kplr
-from kplr.ld import get_quad_coeffs
-
 from bart.data import LightCurve
-
 from . import _kois
-from .ld import QuadraticLimbDarkening
-
-
-def load_system(kepid, lc_window_factor=4, sc_window_factor=4,
-                detrend_window_factor=1.5, min_dataset_size=10, poly_order=1,
-                ldp_nbins=500):
-    client = kplr.API()
-
-    logging.info("Getting the catalog parameters for KIC {0}"
-                 .format(kepid))
-    kois = sorted([k for k in client.star(kepid).kois
-                   if k.koi_disposition in ["CANDIDATE", "CONFIRMED"]],
-                  key=lambda k: k.kepoi_name)
-    if not len(kois):
-        raise RuntimeError("No KOIs listed in the catalog for ID '{0}'"
-                           .format(kepid))
-
-    # Set up the initial limb-darkening profile.
-    teff = kois[0].koi_steff
-    mu1, mu2 = get_quad_coeffs(teff if teff is not None else 5778)
-    ldp = QuadraticLimbDarkening(mu1, mu2, ldp_nbins)
-
-    # Hack to make sure that the parameters are physical.
-    ldp.q1 = min(0.9, max(0.1, ldp.q1))
-    ldp.q2 = min(0.9, max(0.1, ldp.q2))
-
-    # Set up the model.
-    model = Model(ldp, epoch_tol=sc_window_factor,
-                  period_tol=sc_window_factor*3e-4)
-
-    # Loop over KOIs and add the initial values to the model.
-    full_durations = np.array([])
-    for koi in kois:
-        # Parse the KOI parameters.
-        P = koi.koi_period
-        t0 = koi.koi_time0bk % P
-        ror = koi.koi_ror
-        b = koi.koi_impact
-
-        # Skip single transits.
-        if P < 0:
-            continue
-
-        # Convert the KOI duration to the b=0 duration that we need.
-        full_durations = np.append(full_durations, koi.koi_duration/24.)
-        tau = koi.koi_duration/24.
-        # tau = (koi.koi_duration/24.) / np.sqrt((1+ror)**2 - b*b)
-
[…]

### 2013-12-26 kois/kois.py
name of the model

@@ -33,8 +33,9 @@ class KOILightCurve(LightCurve):
 
 class Model(object):
 
-    def __init__(self, ldp, epoch_tol=1.0, period_tol=7e-4, tol=1e-7,
+    def __init__(self, name, ldp, epoch_tol=1.0, period_tol=7e-4, tol=1e-7,
                  max_depth=4):
+        self.name = name
         self.ldp = ldp
         self.datasets = []
 

### 2013-12-26 plot.py
batch scripts

@@ -4,14 +4,9 @@ import subprocess
 
 
 def run_process(kid):
-    if os.path.exists("models/{0}/triangle.png".format(kid)):
-        return None
     try:
-        cmd = "scripts/kois-fetch-results {0}".format(kid)
-        print("Running: {0}".format(cmd))
-        subprocess.check_call(cmd, shell=True)
-
-        cmd = "scripts/kois-plot-results models/{0} -b 20000".format(kid)
+        cmd = ("scripts/kois-plot-results {0} --burnin 20000 "
+               "--triangle").format(kid)
         print("Running: {0}".format(cmd))
         subprocess.check_call(cmd, shell=True)
 
@@ -26,5 +21,5 @@ def run_process(kid):
 
 # pool = Pool()
 results = map(run_process,
-              [int(line.split()[0]) for line in open("targets/kois.txt")])
+              [float(line.strip()) for line in open("targets/kois.txt")])
 print("\n".join(map(str, [r for r in results if r is not None])))

### 2013-12-26 run.py

@@ -5,4 +5,4 @@ def run_process(kid):
     print("Running: {0}".format(cmd))
     subprocess.check_call(cmd, shell=True)
 
-map(run_process, [int(line.split()[0]) for line in open("targets/kois.txt")])
+map(run_process, [line.strip() for line in open("targets/kois.txt")])

### 2013-12-26 document/ms.tex
description of model and parameters

@@
 
+TODO: Talk about the philosophy of interim priors here.
+
+TODO: Justify the use of non-physically motivated parameters and relate this
+to the idea of sufficient statistics.
+
 \section{Data}
@@
 
-A model, from our perspective,
-is a parameterized probability for the data,
-and a prior probability distribution over parameters.
+A model, from our perspective, is a parameterized probability for the data,
+the likelihood function, and a prior probability distribution over parameters.
+We will also divide the likelihood further into a \emph{deterministic physical
+generative model} and a \emph{stochastic noise model}.
+The form for each of these model components can be freely chosen and in the
+next sections, we'll justify our specific choices.
+In short, we assume independent Gaussian noise, a Mandel \& Agol (CITE) like
+limb darkened light curve, and simple interim priors.
+
+\paragraph{Noise model}
+The noise in the light curves generated by the Kepler pipeline result from a
+large collection of effects.
+There are both astrophysical sources (stellar variability, \etc) instrumental
+effects (photon noise, temperature and pointing variations, \etc).
+The exact effect of each of these effects is complicated by the aperture
+photometry procedure and all of the preconditioning steps discussed above.
+Despite these complications, we'll assume that the error bars produced by the
+Kepler pipeline are good estimates and that they are distributed independently
+and normally.
+This is a reasonable assumption because TODO.
+
+\paragraph{Generative model}
+For this project, we assume a quadratic limb darkened light curve model
+following Mandel \& Agol (CITE) and integrate over exposure time (Kipping
+CITE, Appendix XXXX).
+Since we don't want to be dependent on specific stellar parameters and since
+we would like to make it easy to apply any new stellar catalogs, we don't use
+physical orbits.
+Instead, we parameterize the orbit using only ``observable'' parameters.
+In particular, we use, for the star, the mean stellar flux \fstar, and the
+parameters \qone\ and \qtwo\ of a quadratic limb darkening profile
+(parameterized following Kipping CITE).
+For each companion, we parameterize the orbit using period \period, epoch
+\epoch, transit duration \duration, radius ratio \ror, and impact parameter
+\impact.
+
+\paragraph{Interim priors}
+For simplicity---and that is the main goal when using interim priors---we
+chose to model the prior probabilities for each parameter as uniform
+distributions in the linear parameter except the radius ratio.
+For this distribution, we use
+\begin{eqnarray}
+p(\ror) &\propto& \left \{ \begin{array}{ll}
+1/\ror^2 & \ror_\mathrm{min} \le \ror \le 1 \\
+0 & \mathrm{otherwise} \\
+\end{array}\right.
+\end{eqnarray}
+where we conservatively choose $\ror_\mathrm{min} = 10^{-4}$.
+
+\begin{deluxetable}{lclcc}
+\tabletypesize{\footnotesize}
+\tablecolumns{3}
+\tablewidth{0pt}
+
+\tablecaption{%
+The parameters of the generative model and their associated interim priors.
+\tablabel{parameters}}
+
+\tablehead{%
+\colhead{Symbol} &
+\colhead{Unit} &
+\colhead{Description} &
+\colhead{Range} &
+\colhead{Prior}
+}
+
+\startdata
+
+\fstar & --- & mean stellar flux & $[0, 2]$ & Uniform \\
+\qone & --- & first limb darkening coefficient & $[0, 1]$ & Uniform \\
+\vspace{0.5cm}
+\qtwo & --- & second limb darkening coefficient & $[0, 1]$ & Uniform \\
+
+\period & days & orbital period & $[0, 1000]$\tablenotemark{a} & Uniform \\
+\epoch & days & center time of reference transit & $[0, 1000]$\tablenotemark{a}
+       & Uniform \\
+\duration & days & transit duration\tablenotemark{b} & $[0, 10]$ & Uniform \\
+\ror & --- & radius ratio & $[10^{-4}, 1]$ & $1/\ror^2$ \\
+\impact & --- & impact parameter & $[0, 2]$ & Uniform \\
+
+\enddata
+
+\tablenotetext{a}{%
+In practice, we use more constraining priors on \period\ and \epoch\
+because the initial values are very close to correct in most cases but this
+doesn't affect the results.
+}
+\tablenotetext{b}{%
+The transit duration is defined as the time between initial contact and
+final contact.
+}
+\end{deluxetable}
+
 For the probability of the data, we do [XXX chi-squared].

### 2013-12-27 document/ms.tex
NYU HPC ack
swift ack
starting to describe integration method

@@
     Tim Morton (Princeton),
+    Jon Swift (Caltech),
     \ldots
 for helpful contributions to the ideas and code presented here.
+This work made use of the BuTinah cluster supported by NYU HPC (FIXME).
 This project was partially supported by the NSF (grant AST-0908357), and NASA
@@
 
+\appendix
+
+\section{Recursive exposure time integration}
+
+It is well known (Kipping, others, ASK BARCLAY) that integrating the
+exposure time when computing a generative light curve model makes a huge
+difference especially for short period orbits.
+Kipping argues for the use of a resampling technique.
+For computational efficiency and robustness to \emph{contact point
+discontinuities}, we developed and used an adaptive recursive algorithm.
+This algorithm refines the resampling grid around points where where second
+derivative of the light curve function is largest.
+This means that the base grid can be extremely coarse.
+
+The basic idea is that we have some function $f(t)$ that returns the
+instantaneous flux of the system at time $t$ but we would like to compute the
+integrated flux over an exposure time \texp
+\begin{eqnarray}
+f_\mathrm{int}(t_0) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
+\end{eqnarray}
+
 \end{document}

### 2013-12-27 kois/lightcurve.c
small typo in recursive formula

@@ -4,8 +4,6 @@
 #include "lightcurve.h"
 #include "quad.h"
 
-#define LC_FACTOR 0.166666666666666666666666666
-
 double lc_evaluate_one (double t, double p, double t0, double tau, double ror,
                         double b, double mu1, double mu2)
 {
@@ -33,19 +31,20 @@ double lc_integrate (double t, double f0, double texp, int np,
                      double *rors, double *impacts, double mu1, double mu2,
                      double tol, int max_depth, int depth)
 {
-    double tp = t+LC_FACTOR*texp,
-           tm = t-LC_FACTOR*texp,
+    double st = texp/3.0,
+           tp = t+st,
+           tm = t-st,
            fp = lc_evaluate (tp, np, periods, epochs, durations,
                              rors, impacts, mu1, mu2),
            fm = lc_evaluate (tm, np, periods, epochs, durations,
                              rors, impacts, mu1, mu2);
     double d = fabs(fp- 2*f0 + fm);
     if (d > tol && depth < max_depth) {
-        fp = lc_integrate(tp, fp, texp/3.0, np, periods, epochs, durations,
+        fp = lc_integrate(tp, fp, st, np, periods, epochs, durations,
                           rors, impacts, mu1, mu2, tol, depth+1, max_depth);
-        f0 = lc_integrate(t, f0, texp/3.0, np, periods, epochs, durations,
+        f0 = lc_integrate(t, f0, st, np, periods, epochs, durations,
                           rors, impacts, mu1, mu2, tol, depth+1, max_depth);
-        fm = lc_integrate(tm, fm, texp/3.0, np, periods, epochs, durations,
+        fm = lc_integrate(tm, fm, st, np, periods, epochs, durations,
                           rors, impacts, mu1, mu2, tol, depth+1, max_depth);
     }
     return (f0+fp+fm) / 3.0;

### 2013-12-28 document/ms.tex

@@
 \begin{eqnarray}
-f_\mathrm{int}(t_0) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
+f_\mathrm{int}(t_0;\texp) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
+    \quad.
 \end{eqnarray}
+Following Kipping, this can be approximated as
+\begin{eqnarray}
+f_\mathrm{int}(t_0;\texp) &\approx&
+    \frac{f(t_0-\texp/3)+f(t_0)+f(t_0+\texp/3)}{3} \quad.
+\end{eqnarray}
+We extend this by recursively defining this approximation as
+\begin{eqnarray}
+f_\mathrm{int}(t_0;\texp) &\approx&
+    \frac{f_\mathrm{int}(t_0-\texp/3;\texp/3)+f_\mathrm{int}(t_0;\texp/3)
+          +f_\mathrm{int}(t_0+\texp/3;\texp/3)}{3}
+\end{eqnarray}
+where the recursive depth is set by a tolerance on
+\begin{eqnarray}
+\left | f(t_0-\texp/3)-2\,f(t_0)+f(t_0+\texp/3) \right | &\le& \epsilon
+\end{eqnarray}
+where $\epsilon$ is a free parameter quantifying the required accuracy of the
+method.
 

### 2013-12-29 document/ms.tex
initial description of target selection and data selection/preconditioning

@@
 the available light curves from \kepler\ Quarters 0 through 16.
-We release both the catalog values and full $16384$-element posterior samplings for each
-system.
+We release both the catalog values and full $16384$-element posterior
+samplings for each system.
 We compare our results to the existing KOI Catalog and find xxx.
@@
 
-Kepler data here.
+The goal of this project is to propagate any information about exoplanets from
+the \kepler\ light curves into a form that is more user friendly.
+We target the list of all \kepler\ Objects of Interest (KOIs) listed on the
+Exoplanet Archive\footnote{FIXME: URL} as planet candidates and confirmed
+planets from quarters xxx--yyy.
+Some of these candidates are certainly so-called false positives but we treat
+them all equally so that the user can freely make their own target selection.
+As our raw dataset, we start with the MAP-PDC light curves (CITE) provided by
+MAST\footnote{FIXME: URL} and perform further preconditioning or
+``de-trending'' to remove any remaining astrophysical or instrumental noise.
 
-Cut out bits around the transits, masking, etc.
+\paragraph{Target selection}
+We downloaded the full list KOIs from the exoplanet archive using the \kplr\
+Python module\footnote{\url{http://dan.iel.fm/kplr}} on SOME DATE and filtered
+the list to only include planet candidates and confirmed planets as listed in
+the database.
+This list corresponds to the catalog from (SOME CITATION) generated by
+searching the light curves from quarters xxx--yyy using the Transiting Planet
+Search (TPS) module and then hand vetted (CITE).
 
-Pre-conditioning by doing the local linear fits.
+\paragraph{Data selection}
+Next, we downloaded all available PDC light curves (both short and long
+cadence) for a given target and selected all data points within 4 transit
+durations---as determined by the KOI catalog---of a transit.
 
-What gets passed forward:  Flattened light curve bits plus ivars?
+\paragraph{Preconditioning}
+Then, we mask the data within 1.5 transit durations and fit the maximum
+likelihood line to the remaining data points.
+Finally, we divide the full window by this model to generate a ``de-trended''
+light curve.
+This procedure has been applied successfully in the literature (Carter ETC
+CITE) and it should be less destructive to transit signals than alternative
+techniques like median filtering and ``robust'' regression.
 
@@
 \impact.
+\Tab{parameters} specifies the parameters used in this \paper\ and the
+interim priors used.
 
@@
 where we conservatively choose $\ror_\mathrm{min} = 10^{-4}$.
+
+\Tab{parameters} lists the exact interim priors applied to each parameter.
 
@@
 \end{deluxetable}
-
-For the probability of the data, we do [XXX chi-squared].
-
-We choose to sample in parameters that are directly informed by the light
-curve instead of the full set of physical parameters in the generative model.
-The motivation for this choice is to attempt to find parameters that are close
-to sufficient statistics for the light curves while being independent of the
-stellar parameters.
-To this end, we chose to parameterize each planet candidate with period
-\period, epoch \epoch, radius \ror\ (measured in stellar radii), impact
-parameter \impact, and transit duration \duration.
-Our specific definition of transit duration deserves some discussion.
-We define the transit duration as the time that it would take for the
-center of the exoplanet to transit the center of the star (at $b=0$) instead
-of choosing one of the standard definitions---for example $T_\mathrm{tot}$
-from \citet{winn}.
-We make the further simplifying assumption that the planet transits in a
-straight line across the face of the star (WORDING).
-In this limit, the conversion between \duration\ and the standard
-$T_\mathrm{tot}$ used in the KOI catalog is
-\begin{eqnarray}
-T_\mathrm{tot} \approx \duration \, \sqrt{(1+\ror)^2 - \impact^2}
-\end{eqnarray}
 

### 2013-12-30 kois/lightcurve.c
basically nothing

@@ -38,7 +38,7 @@ double lc_integrate (double t, double f0, double texp, int np,
                              rors, impacts, mu1, mu2),
            fm = lc_evaluate (tm, np, periods, epochs, durations,
                              rors, impacts, mu1, mu2);
-    double d = fabs(fp- 2*f0 + fm);
+    double d = fabs(fp - 2*f0 + fm);
     if (d > tol && depth < max_depth) {
         fp = lc_integrate(tp, fp, st, np, periods, epochs, durations,
                           rors, impacts, mu1, mu2, tol, depth+1, max_depth);

### 2014-01-01 kois/database.py
refactoring

@@ -1,0 +1,126 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["db_connection", "init_db", "load_kois"]
+
+import os
+import kplr
+import sqlite3
+from contextlib import closing
+
+
+def database_path():
+    return os.environ.get("KPLR_RESULTS_DIR",
+                          os.path.join("results", "kois.db"))
+
+
+def db_connection():
+    return sqlite3.connect(database_path())
+
+
+def init_db():
+    with closing(db_connection()) as db:
+        db.cursor().executescript(SCHEMA)
+        db.commit()
+
+
+def load_kois():
+    # Get the KOI listing from the Exoplanet Archive.
+    client = kplr.API()
+    kois = client.kois(where="koi_pdisposition+like+'CANDIDATE'")
+
+    with closing(db_connection()) as db:
+        columns = ["kepoi_name", "kepid", "koi_disposition",
+                   "koi_period", "koi_period_err1", "koi_period_err2",
+                   "koi_time0bk", "koi_time0bk_err1", "koi_time0bk_err2",
+                   "koi_ror", "koi_ror_err1", "koi_ror_err2", "koi_impact",
+                   "koi_impact_err1", "koi_impact_err2", "koi_duration",
+                   "koi_duration_err1", "koi_duration_err2", "koi_steff",
+                   "koi_steff_err1", "koi_steff_err2"]
+        db.cursor().executemany("INSERT INTO kois({0}) VALUES ({1})"
+                                .format(",".join(columns),
+                                ",".join(["?" for i in range(len(columns))])),
+                                [map(lambda c: getattr(k, c), columns)
+                                 for k in kois])
+        db.commit()
+
+
+SCHEMA = """
+drop table if exists kois;
+create table kois(
+    id integer primary key,
+    kepoi_name text,
+    kepid integer,
+    koi_disposition text,
+    koi_period real,
+    koi_period_err1 real,
+    koi_period_err2 real,
+    koi_time0bk real,
+    koi_time0bk_err1 real,
+    koi_time0bk_err2 real,
+    koi_ror real,
+    koi_ror_err1 real,
+    koi_ror_err2 real,
+    koi_impact real,
[…]

### 2014-01-01 kois/kois.py

@@ -8,7 +8,7 @@ __all__ = ["LightCurve", "Model"]
 
 import numpy as np
 from bart.data import LightCurve
-from . import _kois
+from .lightcurve import _kois
 
 
 class KOILightCurve(LightCurve):

### 2014-01-01 setup.py

@@ -5,13 +5,15 @@ import numpy
 from setuptools import setup, Extension
 
 includes = [
-    "kois",
+    "kois/lightcurve",
+    "/share/apps/boost/1.49.0/intel/serial/include",
     "boost_1_55_0",
     numpy.get_include(),
 ]
 
-kois = Extension("kois._kois", ["kois/_kois.c", "kois/lightcurve.c",
-                                "kois/quad.cpp"],
+kois = Extension("kois.lightcurve._kois", ["kois/lightcurve/_kois.c",
+                                           "kois/lightcurve/lightcurve.c",
+                                           "kois/lightcurve/quad.cpp"],
                  include_dirs=includes)
 
 setup(

### 2014-01-01 kois/__init__.py
more general configurations

@@ -2,4 +2,4 @@
 # -*- coding: utf-8 -*-
 
 from __future__ import absolute_import
-from .kois import *
+from .build_model import build_model

### 2014-01-01 kois/build_model.py

@@ -1,0 +1,77 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = ["build_model"]
+
+import logging
+import numpy as np
+
+import kplr
+from kplr.ld import get_quad_coeffs
+
+from .lightcurve.ld import QuadraticLimbDarkening
+from .kois import Model, KOILightCurve
+
+
+def build_model(koi_id, window_factor=4.0, detrend_factor=1.5, poly_order=1):
+    # Set up the model.
+    client = kplr.API()
+    koi = client.koi(koi_id)
+    assert koi.koi_disposition in ["CANDIDATE", "CONFIRMED"], \
+        "That KOI is not a candidate or confirmed system"
+
+    # Limb darkening and initial model.
+    teff = koi.koi_steff
+    mu1, mu2 = get_quad_coeffs(teff if teff is not None else 5778)
+    ldp = QuadraticLimbDarkening(mu1, mu2)
+    ldp.q1 = min(0.9, max(0.1, ldp.q1))
+    ldp.q2 = min(0.9, max(0.1, ldp.q2))
+    model = Model("KOI {0}".format(koi_id), ldp, epoch_tol=window_factor,
+                  period_tol=window_factor*3e-4)
+
+    # Download and trim the datasets.
+    model.add_koi(koi.koi_period, koi.koi_time0bk % koi.koi_period,
+                  koi.koi_duration / 24.0, koi.koi_ror, koi.koi_impact)
+
+    # Load the light curves.
+    logging.info("Loading datasets")
+    datasets = []
+    for lc in koi.get_light_curves():
+        try:
+            data = lc.read()
+        except:
+            continue
+        m = data["SAP_QUALITY"] == 0
+        texp = (kplr.EXPOSURE_TIMES[1] if lc.sci_archive_class == "CLC"
+                else kplr.EXPOSURE_TIMES[0])
+        window = np.array([max(window_factor*d,
+                           window_factor*d+5*kplr.EXPOSURE_TIMES[1]/86400.)
+                           for d in model.durations])
+        data = KOILightCurve(data["TIME"][m],
+                             data["PDCSAP_FLUX"][m],
+                             data["PDCSAP_FLUX_ERR"][m], texp=texp,
+                             K=5 if lc.sci_archive_class == "CLC" else 3)
+        datasets += (data.active_window(model.periods, model.epochs,
[…]

### 2014-01-01 kois/database.py

@@ -4,35 +4,23 @@
 from __future__ import (division, print_function, absolute_import,
                         unicode_literals)
 
-__all__ = ["db_connection", "init_db", "load_kois"]
+__all__ = ["init_db", "load_kois"]
 
-import os
 import kplr
 import sqlite3
-from contextlib import closing
 
 
-def database_path():
-    return os.environ.get("KPLR_RESULTS_DIR",
-                          os.path.join("results", "kois.db"))
-
-
-def db_connection():
-    return sqlite3.connect(database_path())
-
-
-def init_db():
-    with closing(db_connection()) as db:
+def init_db(dbpath):
+    with sqlite3.connect(dbpath) as db:
         db.cursor().executescript(SCHEMA)
-        db.commit()
 
 
-def load_kois():
+def load_kois(dbpath):
     # Get the KOI listing from the Exoplanet Archive.
     client = kplr.API()
     kois = client.kois(where="koi_pdisposition+like+'CANDIDATE'")
 
-    with closing(db_connection()) as db:
+    with sqlite3.connect(dbpath) as db:
         columns = ["kepoi_name", "kepid", "koi_disposition",
                    "koi_period", "koi_period_err1", "koi_period_err2",
                    "koi_time0bk", "koi_time0bk_err1", "koi_time0bk_err2",
@@ -43,9 +31,11 @@ def load_kois():
         db.cursor().executemany("INSERT INTO kois({0}) VALUES ({1})"
                                 .format(",".join(columns),
                                 ",".join(["?" for i in range(len(columns))])),
-                                [map(lambda c: getattr(k, c), columns)
+                                [map(lambda c: getattr(k, c)
+                                     if c != "kepoi_name"
+                                     else unicode(float(k.kepoi_name[1:])),
+                                     columns)
                                  for k in kois])
-        db.commit()
 
 
 SCHEMA = """
@@ -74,14 +64,13 @@ create table kois(
     koi_steff_err1 real,
     koi_steff_err2 real,
     submitted text,
-    secret text,
     remote_id text,
-    completed text,
     fetched text,
     plotted text,
     comments text,
     nwalkers integer,
     steps integer,
+    burnin integer,
     acor_time real,
     map_fstar real,
     map_q1 real,
@@ -117,10 +106,3 @@ create table kois(
     kplr_impact_err2 real
 );
 """
-
-
-if __name__ == "__main__":
-    print("Setting up schema")
-    init_db()
-    print("Loading KOIs")
-    load_kois()

### 2014-01-12 iterative_benchmark.py
starting iterative benchmark

@@ -1,0 +1,13 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from __future__ import (division, print_function, absolute_import,
+                        unicode_literals)
+
+__all__ = []
+
+import numpy as np
+
+P = 150.0
+t = np.concatenate([i*P + np.arange(0.0, 10.0, 0.5/24.) for i in range(4)])
+print(t)

### 2014-01-12 iterative_benchmark.py
testing scalings w various parameters

@@ -6,8 +6,25 @@ from __future__ import (division, print_function, absolute_import,
 
 __all__ = []
 
+import time
+import kplr
 import numpy as np
 
+from kois.kois import Model
+from kois.lightcurve.ld import QuadraticLimbDarkening
+
 P = 150.0
-t = np.concatenate([i*P + np.arange(0.0, 10.0, 0.5/24.) for i in range(4)])
-print(t)
+t = np.concatenate([i*P + np.arange(0.0, 10.0, 0.5/24.) for i in range(100)])
+
+ldp = QuadraticLimbDarkening(0.3, 0.1)
+model = Model("test", ldp, tol=1e-20, max_depth=10000)
+model.add_koi(P, 5.0, 13.0 / 24.0, 0.5, 0.8)
+
+print(model.durations)
+texp = kplr.EXPOSURE_TIMES[1]/86400.0
+
+for tau in [0.05, 0.1, 0.5, 1.0]:
+    model.durations[0] = tau
+    strt = time.time()
+    lc = model.get_light_curve(t, texp=texp)
+    print(tau, time.time() - strt)

### 2014-01-14 iterative_benchmark.py
updating code and document to use 'slow-roll' condition

@@ -9,22 +9,51 @@ __all__ = []
 import time
 import kplr
 import numpy as np
+import matplotlib.pyplot as pl
 
 from kois.kois import Model
 from kois.lightcurve.ld import QuadraticLimbDarkening
 
 P = 150.0
-t = np.concatenate([i*P + np.arange(0.0, 10.0, 0.5/24.) for i in range(100)])
+# t = np.concatenate([i*P + np.arange(0.0, 10.0, 0.5/24.) for i in range(100)])
 
 ldp = QuadraticLimbDarkening(0.3, 0.1)
-model = Model("test", ldp, tol=1e-20, max_depth=10000)
-model.add_koi(P, 5.0, 13.0 / 24.0, 0.5, 0.8)
+model = Model("test", ldp, tol=1e-12, max_depth=50)
+# model.add_koi(P, 0.0, 12.0 / 24.0, 0.04, 0.7)
+model.add_koi(P, 0.0, 0.4 / 24.0, 0.04, 0.7)
 
-print(model.durations)
 texp = kplr.EXPOSURE_TIMES[1]/86400.0
+print(texp)
 
-for tau in [0.05, 0.1, 0.5, 1.0]:
-    model.durations[0] = tau
+t = np.linspace(-1, 1, 10013)
+# t = 0.02 - 0.04 * np.sort(np.random.rand(200))
+
+lcs = []
+for tol, md, fmt in [(0.0, 1, "-r"),
+                     (0.0, 2, "--k"),
+                     (0.0, 3, "--k"),
+                     ]:
+    print(fmt)
+    model.tol = tol
+    model.max_depth = md
+
     strt = time.time()
-    lc = model.get_light_curve(t, texp=texp)
-    print(tau, time.time() - strt)
+    lcs.append(model.get_light_curve(t, texp=texp))
+    print(time.time() - strt)
+
+pl.plot(t, lcs[2] - lcs[0], "k")
+pl.plot(t, lcs[2] - lcs[1], "r")
+
+pl.xlim(-0.03, 0.03)
+# pl.ylim(0.9987, 1.0002)
+pl.savefig("diff.png")
+
+
+
+# print(model.durations)
+
+# for tau in [0.05, 0.1, 0.5, 1.0]:
+#     model.durations[0] = tau
+#     strt = time.time()
+#     lc = model.get_light_curve(t, texp=texp)
+#     print(tau, time.time() - strt)

### 2014-01-14 kois/lightcurve/lightcurve.c

@@ -40,7 +40,7 @@ double lc_integrate (double t, double f0, double texp, int np,
                              rors, impacts, mu1, mu2),
            fm = lc_evaluate (tm, np, periods, epochs, durations,
                              rors, impacts, mu1, mu2),
-           d = fabs(fp - 2*f0 + fm);
+           d = fabs((fp - 2*f0 + fm) / (fp - fm));
 
     if (d > tol && depth < max_depth) {
         fp = lc_integrate(tp, fp, st, np, periods, epochs, durations,

### 2014-01-14 kois/lightcurve/quad.cpp

@@ -143,6 +143,7 @@ double ldlc (double p, double z, double u1, double u2)
 #ifdef VERBOSE
                 printf("Case 12 - FIXME\n");
 #endif
+                printf("Case 12 - FIXME\n");
                 // FIXME.
                 ld = 0.0;
             } else {

### 2014-01-14 document/ms.tex
updating code and document to use 'slow-roll' condition
'outline' of method section

@@
 
+\section{Sampling method}
+
+We sampled the posterior probability in equation SOMEEQN using the affine
+invariant ensemble sampler (CITE: GW, emcee).
+This method is perfect for this project because it tends to require very
+little tuning even when applied to new datasets.
+
+\paragraph{Ensemble specifications}
+We run with 48 walkers on 24 cores on the BuTinah cluster at NYUAD.
+
+\paragraph{Initialization}
+We start sampling in a \emph{tiny} isotropic Gaussian ball (HOW BIG) centered
+at the parameters given in the KOI catalog.
+Then, we run 2000 iterations of MCMC and re-sample the walkers in a similarly
+time Gaussian ball around the maximum probability point seen in that run.
+
+\paragraph{Production chain}
+Finally we run the production chain---re-estimating the integrated
+auto-correlation time for each parameter---until we have at least $128 \times
+N_\mathrm{walkers}$ independent samples for ever parameter.
+
+\paragraph{Analysis of convergence}
+
+\section{Results}
+
 \section{The empirical radius distribution}
@@
 \begin{eqnarray}
-\left | f(t_0-\texp/3)-2\,f(t_0)+f(t_0+\texp/3) \right | &\le& \epsilon
+\left | \frac{f(t_0-\texp/3)-2\,f(t_0)+f(t_0+\texp/3)}
+             {f(t_0-\texp/3)-f(t_0+\texp/3)} \right | &\le& \epsilon
 \end{eqnarray}

### 2014-01-14 kois/kois.py
automatically determine burn-in using acorr time

@@ -33,8 +33,8 @@ class KOILightCurve(LightCurve):
 
 class Model(object):
 
-    def __init__(self, name, ldp, epoch_tol=1.0, period_tol=7e-4, tol=1e-8,
-                 max_depth=10):
+    def __init__(self, name, ldp, epoch_tol=1.0, period_tol=7e-4, tol=0.1,
+                 max_depth=2):
         self.name = name
         self.ldp = ldp
         self.datasets = []

### 2014-01-14 plot_all.py

@@ -1,0 +1,26 @@
+import sqlite3
+import subprocess
+
+
+def run_process(kid):
+    try:
+        cmd = ("scripts/kois-plot-results {0} {1} --burnin 2000 "
+               "--triangle").format(kid, "template.cfg")
+        print("Running: {0}".format(cmd))
+        subprocess.check_call(cmd, shell=True)
+
+    except Exception as e:
+        print("{0} FAILED".format(kid))
+        print(e)
+
+    else:
+        print("finished {0}".format(kid))
+        return kid
+
+
+with sqlite3.connect("results/kois.db") as conn:
+    c = conn.cursor()
+    c.execute("select kepoi_name from kois where submitted is not null")
+    kids = map(lambda o: o[0], c.fetchall())
+
+results = map(run_process, kids)

### 2014-01-14 plot_inference.py

@@ -1,0 +1,20 @@
+import numpy as np
+import matplotlib.pyplot as pl
+
+fn = "rdist_samples.txt"
+bins = []
+for line in open(fn):
+    bins += line.strip().strip("]").split("[")[-1].split()
+    if "]" in line:
+        break
+
+bins = np.array(bins, dtype=float)
+samples = np.loadtxt(fn, skiprows=10007)[:, 1:-1]
+
+samples = np.concatenate((samples, 1-np.atleast_2d(np.sum(samples, axis=1)).T),
+                         axis=1)
+
+b = np.array(zip(bins[:-1], bins[1:])).T
+v = np.median(samples, axis=0)
+pl.plot(b.T.flatten(), np.array(zip(v, v)).flatten())
+pl.savefig("ror_inference.png")

### 2014-01-14 run_all.py

@@ -1,0 +1,19 @@
+import sqlite3
+import subprocess
+
+
+def run_process(kid):
+    cmd = "scripts/kois-build-model {0} template.cfg --submit".format(kid)
+    print("Running: {0}".format(cmd))
+    subprocess.check_call(cmd, shell=True)
+
+
+with sqlite3.connect("results/kois.db") as conn:
+    c = conn.cursor()
+    c.execute("select kepoi_name from kois where submitted is null")
+    kids = map(lambda o: o[0], c.fetchall())
+
+print(len(kids))
+assert 0
+
+map(run_process, kids)

### 2014-01-15 plot_all.py
automatically determine burn-in using acorr time

@@ -3,9 +3,10 @@ import subprocess
 
 
 def run_process(kid):
+    print("STARTING {0}".format(kid))
     try:
-        cmd = ("scripts/kois-plot-results {0} {1} --burnin 2000 "
-               "--triangle").format(kid, "template.cfg")
+        cmd = ("scripts/kois-plot-results {0} {1} --triangle"
+               .format(kid, "template.cfg"))
         print("Running: {0}".format(cmd))
         subprocess.check_call(cmd, shell=True)
 

### 2014-01-15 kois/kois.py
switching to better least squares solver, adding L2 reg for detrending

@@ -13,7 +13,7 @@ from .lightcurve import _kois
 
 class KOILightCurve(LightCurve):
 
-    def remove_polynomial(self, periods, epochs, durations, order=1):
+    def remove_polynomial(self, periods, epochs, durations, order=1, l2=0.0):
         t = self.time
         m = np.ones_like(t, dtype=bool)
         for p, t0, dt in zip(periods, epochs, durations):
@@ -23,7 +23,11 @@ class KOILightCurve(LightCurve):
         if np.sum(m) < 10:
             return False
 
-        p = np.polyfit(t[m], self.flux[m], order, w=self.ivar[m])
+        e = np.sqrt(self.ivar[m])
+        A = e[:, None]*np.vander(t[m], order+1)
+        A = np.concatenate((A, l2*np.ones((1, order+1))), axis=0)
+        y = np.append(e*self.flux[m], 0.0)
+        p, residuals, rank, sing_vals = np.linalg.lstsq(A, y)
         self.flux /= np.polyval(p, t)
         return True
 

### 2014-01-16 kois/build_model.py
saner defaults and clearer plot

@@ -52,8 +52,7 @@ def build_model(koi_id, window_factor=4.0, detrend_factor=1.5, poly_order=1):
                            for d in model.durations])
         data = KOILightCurve(data["TIME"][m],
                              data["PDCSAP_FLUX"][m],
-                             data["PDCSAP_FLUX_ERR"][m], texp=texp,
-                             K=5 if lc.sci_archive_class == "CLC" else 3)
+                             data["PDCSAP_FLUX_ERR"][m], texp=texp)
         datasets += (data.active_window(model.periods, model.epochs,
                                         window)
                      .autosplit())

### 2014-01-16 kois/kois.py

@@ -13,7 +13,7 @@ from .lightcurve import _kois
 
 class KOILightCurve(LightCurve):
 
-    def remove_polynomial(self, periods, epochs, durations, order=1, l2=0.0):
+    def remove_polynomial(self, periods, epochs, durations, order=1, l2=1.0):
         t = self.time
         m = np.ones_like(t, dtype=bool)
         for p, t0, dt in zip(periods, epochs, durations):

### 2014-02-03 kois/kois.py
min number of +/- points for de-trend

@@ -13,14 +13,20 @@ from .lightcurve import _kois
 
 class KOILightCurve(LightCurve):
 
-    def remove_polynomial(self, periods, epochs, durations, order=1, l2=1.0):
+    def remove_polynomial(self, periods, epochs, durations, order=1, l2=1.0,
+                          nmin=10):
         t = self.time
         m = np.ones_like(t, dtype=bool)
+        counts = [0, 0]
         for p, t0, dt in zip(periods, epochs, durations):
             hp = 0.5 * p
-            m[np.abs((t - t0 + hp) % p - hp) < dt] = 0
+            d = (t - t0 + hp) % p - hp
+            m0 = np.abs(d) < dt
+            counts[0] += np.sum(d[m0] < 0)
+            counts[1] += np.sum(d[m0] > 0)
+            m[m0] = 0
 
-        if np.sum(m) < 10:
+        if counts[0] < nmin or counts[1] < nmin:
             return False
 
         e = np.sqrt(self.ivar[m])

### 2014-02-03 kois/build_model.py
more conservative splitting and less conservative de-trending

@@ -45,17 +45,18 @@ def build_model(koi_id, window_factor=4.0, detrend_factor=1.5, poly_order=1):
         except:
             continue
         m = data["SAP_QUALITY"] == 0
-        texp = (kplr.EXPOSURE_TIMES[1] if lc.sci_archive_class == "CLC"
-                else kplr.EXPOSURE_TIMES[0])
+        is_lc = lc.sci_archive_class == "CLC"
+        texp = kplr.EXPOSURE_TIMES[1] if is_lc else kplr.EXPOSURE_TIMES[0]
         window = np.array([max(window_factor*d,
                            window_factor*d+5*kplr.EXPOSURE_TIMES[1]/86400.)
                            for d in model.durations])
         data = KOILightCurve(data["TIME"][m],
-                             data["PDCSAP_FLUX"][m],
-                             data["PDCSAP_FLUX_ERR"][m], texp=texp)
+                             data["SAP_FLUX"][m],
+                             data["SAP_FLUX_ERR"][m], texp=texp)
+        data.is_lc = is_lc
         datasets += (data.active_window(model.periods, model.epochs,
                                         window)
-                     .autosplit())
+                     .autosplit(ttol=1.5))
 
     # Remove datasets with not enough data points.
     datasets = [d for d in datasets if len(d.time) > 10]
@@ -68,7 +69,8 @@ def build_model(koi_id, window_factor=4.0, detrend_factor=1.5, poly_order=1):
                        if d.remove_polynomial(model.periods, model.epochs,
                                               detrend_factor
                                               * model.durations,
-                                              poly_order)]
+                                              poly_order,
+                                              nmin=10 if d.is_lc else 30)]
     logging.info("{0} datasets were de-trended".format(len(model.datasets)))
     if not len(datasets):
         raise RuntimeError("No datasets could be de-trended.")

### 2014-02-03 kois/kois.py

@@ -34,7 +34,11 @@ class KOILightCurve(LightCurve):
         A = np.concatenate((A, l2*np.ones((1, order+1))), axis=0)
         y = np.append(e*self.flux[m], 0.0)
         p, residuals, rank, sing_vals = np.linalg.lstsq(A, y)
-        self.flux /= np.polyval(p, t)
+        model = np.polyval(p, t)
+        if np.any(model == 0):
+            return False
+
+        self.flux /= model
         return True
 
     def lnlike(self, light_curve):

### 2014-02-03 document/ms.tex
some words

@@
 \paragraph{Preconditioning}
-Then, we mask the data within 1.5 transit durations and fit the maximum
-likelihood line to the remaining data points.
-Finally, we divide the full window by this model to generate a ``de-trended''
-light curve.
-This procedure has been applied successfully in the literature (Carter ETC
+These light curves still include some systematic noise and stellar
+variability.
+To remove this signal, we mask the data within 1.5 transit durations and find
+the maximum likelihood cubic polynomial trend conditioned on the remaining
+measurements.
+In order to avoid over-fitting, we apply a weak L2 regularization to the
+likelihood:
+\begin{eqnarray}
+\ell(\bvec{c}) &=& -\frac{1}{2}\sum_{n=1}^N \frac{[f_n - m(t_n; \bvec{c})]^2}
+                                                 {\sigma_n^2}
+                   -\frac{\lambda}{2} \left | \bvec{c} \right |^2
+\end{eqnarray}
+where
+\begin{eqnarray}
+m(t_n;\bvec{c}) &=& c_0 + c_1\,t_n + c_2\,t_n^2 + c_3\,t_n^3 \quad.
+\end{eqnarray}
+In practice, after some extremely scientific experiments, we chose to use
+$\lambda = 1$ for every light curve.
+
+Finally, we divide the full window of observations by the predicted trend
+$m(t_n;\bvec{c})$ to produce a ``de-trended'' light curve.
+A similar procedure has been applied successfully in the literature (Carter ETC
 CITE) and it should be less destructive to transit signals than alternative
@@
 For this project, we assume a quadratic limb darkened light curve model
-following Mandel \& Agol (CITE) and integrate over exposure time (Kipping
-CITE, Appendix XXXX).
+following Mandel \& Agol (CITE) and integrate over exposure time using an
+adaptive algorithm described in Appendix (XXXX).
 Since we don't want to be dependent on specific stellar parameters and since
-we would like to make it easy to apply any new stellar catalogs, we don't use
-physical orbits.
+we would like to make it easy to apply any new constraints on the stellar
+parameters, we don't require physical orbits.
 Instead, we parameterize the orbit using only ``observable'' parameters.
+This is a somewhat controversial choice as we will discuss in Section (YYYY).
+
 In particular, we use, for the star, the mean stellar flux \fstar, and the
-parameters \qone\ and \qtwo\ of a quadratic limb darkening profile
-(parameterized following Kipping CITE).
+parameters \qone\ and \qtwo\ of a quadratic limb darkening profile.
+The limb darkening law is parameterized following Kipping (CITE) and the
+coefficients are related to the standard parameterization
+\begin{eqnarray}
+I(\mu) &=& 1 - u_1\,(1-\mu) - u_2\,(1-\mu)^2 \\
+\mu &=& \sqrt{1-r^2}
+\end{eqnarray}
+by
+\begin{eqnarray}
+q_1 &=& (u_1 + u_2)^2 \\
+q_2 &=& \frac{u_1}{2\,(u_1+u_2)} \quad.
+\end{eqnarray}
 For each companion, we parameterize the orbit using period \period, epoch
